---
title: "Credentials"
author: ""
date: ""
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
editor_options:
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Credentials}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Required credentials

Every call to an exported `smartabaseR` functions requires a `url`, `username` and `password`. Note: usernames and emails are **not** interchangeable; `smartabaseR` only accepts valid Smartabase usernames.

### Credential storage

In the `smartabaseR` documentation, we supply credentials in plain text directly in all the examples. We only do this for the sake of space, but in production environments we would advise against storing Smartabase credentials in plain text anywhere, let alone in the main function call for all to see.

Here is some excellent documentation that explores some options: https://cran.r-project.org/web/packages/httr/vignettes/secrets.html.

We'd like to reiterate something Hadley Wickham says in that document: "Regardless of how you store them, to use your secrets you will still need to read them into R variables. Be careful not to expose them by printing them or saving them to a file."

#### Environment variables

At worst, we would suggest storing credentials as environment variables. These are still stored as plain text, but at least they don't need to be shown on screen when using `smartabaseR` in an interactive environment. 

```{r environment_variable_example1, echo = TRUE, eval = FALSE}
## Opens .Reviron file
file.edit("~/.Renviron")
```

If we set the environment variables `SB_URL`, `SB_USER` and `SB_PASS`, then in our script we could call those credentials like this:

```{r environment_variable_example2, echo = TRUE, eval = FALSE}
sb_get_event(
  form = "Training Log",
  date_range = c("01/03/2023", "07/03/2023"),
  url = Sys.getenv("SB_URL"),
  username = Sys.getenv("SB_USER"),
  password = Sys.getenv("SB_PASS")
)
```

#### keyring

A better option is to use a package like [keyring](https://github.com/r-lib/keyring]) which gives you more control over how your secrets are accessed.

#### Ask every time

A more laborious option is to request for a password every time: [rstudioapi::askForPassword()](https://rstudio.github.io/rstudioapi/reference/askForPassword.html) or [getPass::getPass()](https://github.com/wrathematics/getPass).

