---
title: "Retrieving a License Audit"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
editor_options:
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Retrieving a License Audit}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

The `sb_get_license_audit()` function allows administrators to retrieve a license audit from AMS, providing an overview of user access and licensing details.

This function requires authentication and an active session. The resulting license audit file is returned as a tibble.

## Prerequisites

Before using this function, ensure that:
- You have valid login credentials for AMS.
- You have established a session using `sb_login()`.
- You have the necessary permissions to access license audit data.

## Usage

```{r license_audit_example, eval = FALSE}
url <- "example.smartabase.com/example"
username <- "<admin_username>"
password <- "<admin_password>"

login <- sb_login(
  url = url,
  username = username,
  password = password
)

license_audit <- sb_get_license_audit(
  login = login,
  url = url,
  username = username,
  password = password
)

head(license_audit)
```

