---
title: "Get Started"
author: ""
date: ""
output: 
  rmarkdown::html_vignette
editor_options:
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Load smartabaseR

```{r load-package, eval = FALSE}
library(smartabaseR)
```

## Requirements

`smartabaseR` can only be used on Smartabase versions **6.14** or greater (if your account has `superadmin` or `site owner` privileges, then `smartabaseR` can also be used with **v6.13**). 

In 2023, Smartabase switched to [calendar versioning](https://calver.org/). `smartabaseR` can be used on any site that uses calendar versioning e.g. **2023.1**, **2023.2** etc.

### Credentials

Please see `vignette("credentials")`.

### Exporting data from Smartabase
Exporting Smartabase data with `smartabaseR` is easy with the `sb_get_event()` function. You will at a minimum need to supply values to the `form`, `date_range`, `url`, `username` and `password` arguments. Note that `date_range` contains a `start_date` and an `end_date` and each must be in dd/mm/YYYY format.

```{r export_example1, eval = FALSE}
sb_get_event(
  form = "Training Log",
  date_range = c("01/03/2023", "07/03/2023"),
  url = "example.smartabase.com/site",
  username = "example.username", # note: must be valid username, not email
  password = "example_password"
)
```

```{r  export_success, echo = FALSE}                  
cli::cli_alert_success(
  "Successfully logged example.username into example.smartabase.com/site."
)
cli::cli_alert_success("User details export successful.")      
cli::cli_alert_success(
  "Training Log export successful (Mar 03 2020 - Mar 07 2023)."
)
```

A successful export! We have `Training Log` data for two athletes named Aiden Thomas and Jamie Anderson.

```{r fake_data, echo = FALSE, paged.print = TRUE}
training_data <- dplyr::tibble(
  start_date = "03/01/2023",
  user_id = c(37204, 37201),
  about = c("Aiden Thomas", "Jamie Anderson"),
  distance = c(2530, 5411),
  rpe = c(5, 7),
  event_id = c(2381840, 2382033),
  entered_by_user_id = c(37204, 37201)
)

training_data
```

**Note**, frequently exporting data (especially large data sets) can put stress on your Smartabase server which may affect your organisation's Smartabase experience. At a minimum, please save your exported data to a variable (here we saved it to a variable called "training_data"). This minimises unnecessary API calls.

## Importing data to Smartabase
We can also import an R data frame into Smartabase using `sb_insert_event()`.

Imagine we want to calculate the difference between each athlete's RPE and the team average RPE and upload the results to a form called "Team Summary" 

First, to calculate the team average:

```{r avg_rpe, message = FALSE}
# Need to load dplyr
library(dplyr)

rpe_average <- training_data %>% 
  select(-entered_by_user_id) %>% 
  mutate(team_rpe = round(mean(rpe), 1))

rpe_average
```

Now to compare the group average to each athlete's RPE:

```{r}
rpe_average <- rpe_average %>%
  mutate(rpe_diff = rpe - team_rpe)

rpe_average
```

Finally, to upload our results back up to Smartabase, we need to supply a data frame and a form name as well as our credentials:

```{r insert_rpe, eval = FALSE}
sb_insert_event(
  df = rpe_average,
  form = "Team Summary",
  url = "example.smartabase.com/site",
  username = "example.username", # note: must be valid username, not email
  password = "example_password"
)
```

```{r insert_rpe_success, echo = FALSE}
cli::cli_alert_success(
  "SUCCESSFULLY_INSERTED: 2 out of 2 records successfully inserted into \\
  Team Summary."
)
```

Success! Our data should now be imported into the "Team Summary" form on Smartabase.

To learn more about how to get the most out of `smartabaseR`, please see the `exporting-data` and `importing-data` vignettes.
