---
title: "Helper Functions"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
editor_options:
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Helper Functions}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

If you haven't already, please read the `vignette("get-started")` before preceding.

`smartabaseR` contains several helper functions that are called from other exported functions. The two main ones are `sb_get_user()` and `sb_get_group()`.

## sb_get_user()

`sb_get_user()` leverages the Smartabase API to get user data out of Smartabase and into your R session. User data includes identifying information like user ID, about, first/last name, username and email. If the `include_all_cols` option is to `TRUE`, extra user information is included like phone numbers, addresses, UUIDs and groups/roles information.

Furthermore, you can filter for certain users via the `user_key` and `user_value` filters. Note: if these arguments are left empty, then all data for every user you have access to will be returned.

Why is `sb_get_user()` useful? Recall that the Smartabase API requires athletes' user IDs when importing into Smartabase with `sb_insert_event()` etc. (see `vignette("importing-data")`). `sb_get_user()` is just one way to find your athletes' user IDs for use with `sb_insert_event()` and the rest of the import functions.

### filter

#### user_key/user_value

`user_key` and `user_value` allow you to get user data for specific Smartabase users.

`user_key` represents the user identification method: "about", "user_id", "username" or "email". 

**about**

All `filter` values must be generated by the relevant helper function. So, if we're using `sb_get_user()` to export user data only for the athlete `Jamie Anderson`, we would need to use `sb_get_user_filter()` along with the `user_key` and `user_value` options:

```{r filter_example, eval = FALSE}
sb_get_user(
  url = "example.smartabase.com/site",
  username = "example.username",
  password = "example_password",
  filter = sb_get_user_filter(
    user_key = "about",
    user_value = "Jamie Anderson"
  )
)
```

If `user_key = "about"`, `data_value` accepts *full names*.

See `vignette("exporting-data")` for a breakdown of the other possible `user_key` arguments. 


### option

#### include_all_cols

By default, `sb_get_user()` returns `user_id`, `first_name`, `last_name`, `username` and `email`, for each user. However, if we set `include_all_cols` to `TRUE` within `sb_get_user_option()`, then `dob`, `middle_name`, `known_as`, `sex`, `phone` and `address` is also returned. 

Note: `phone` and `address` are returned as lists of tibbles. 

Note #2: if only a single athlete is returned in the payload, then `group` and `role` columns (lists of tibbles) are also returned.

```{r option_example1_data, include = FALSE}

athlete_group_list <- list(
  tibble::tibble(
    athlete_group_id = c(1, 9),
    athlete_group_name = c("Example Group 1", "Example Group 2")
  )
)

coach_group_list <- list(
  tibble::tibble(
    coach_group_id = c(1, 9, 21),
    coach_group_name = c(
      "Example Group 1",
      "Example Group 2",
      "Example Group 3"
    )
  )
)

role_list <- list(
  tibble::tibble(
    role_id = 1,
    role_name = "Example Role 1"
  )
)

phone_list <- list(
  tibble::tibble(
    phone_type_count = c(1, 2, 1),
    phone_type = c("phone_home", "phone_home", "phone_emergency"),
    phone_number = c(12341234, 45674567, 67896789)
  )
)

address_list <- list(
  tibble::tibble(
    address_type_count = c(1, 1, 2),
    address_type = c(
      "address_primary",
      "address_alternative", 
      "address_alternative"
    ),
    address = c(
      "North Tower, Level 1/339 Coronation Dr, Milton QLD 4064",
      "76 Neon St Sumner QLD 4064",  
      "76 Neon St Sumner QLD 4064"
    )
  )
)

user_data <- tibble::tibble(
  user_id = 12000,
  about = "Jamie Anderson",
  first_name = "Jamie",
  last_name = "Anderson",
  username = "jamie.anderson",
  email = "jamie.anderson@teamworks.com",
  dob = "01/01/2000",
  middle_name = "",
  known_as = "",
  sex = "MALE",
  athlete_group = athlete_group_list,
  coach_group = coach_group_list,
  role = role_list,
  phone = phone_list,
  address = address_list
)
```

```{r option_example1, eval = FALSE}
user_data <- sb_get_user(
  url = "example.smartabase.com/site",
  username = "example.username",
  password = "example_password",
  filter = sb_get_user_option(
    include_all_cols = TRUE
  )
)
user_data
```

```{r option_example2, echo = FALSE}
user_data
```

To unnest a list column, you can use the `unnest()` from `tidyr`:

```{r option_example3}
tidyr::unnest(user_data, athlete_group)
```

## sb_get_group()

`sb_get_group()` returns a list of Smartabase groups available to your account. It's arguments are `username`, `password` and `url`.

```{r, get_group, eval = FALSE}
get_group(
  url = "example.smartabase.com/site",
  username = "example.username",
  password = "example_password"
)
```

```{r get_group_print, echo = FALSE}
groups_df <- dplyr::tibble(
  group = c("All Users", "First Team", "Reserves")
)

groups_df
```


## sb_select_metadata() 

Once data has been exported from Smartabase, it is often desirable to retain the metadata variables (e.g. about, start_time etc.) in the data frame before importing back to Smartabase. This helper function will look for any metadata variables present in a data frame and return them, as opposed to needing to write out write out metadata variables names yourself. For example:

```{r get_metadata_names_example, eval = FALSE}
example_df <- dplyr::tibble(
  about = c("Jamie Anderson", "Charlie Thompson"),
  start_date = c("14/02/2023", "14/02/2023"),
  form = "Hydration",
  `Body Weight pre training` = round(runif(2, 82, 92), 0),
  `Body Weight post training` = round(runif(2, 82, 92), 0),
  `Urine Colour` = round(runif(2, 1, 8), 0),
  end_date = c("14/02/2023", "14/02/2023")
)

example_df %>% dplyr::select(sb_select_metadata(.))
```


```{r get_metadata_names_example2, echo = FALSE}
dplyr::tibble(
  about = c("Jamie Anderson", "Charlie Thompson"),
  start_date = c("14/02/2023", "14/02/2023"),
  form = "Hydration",
  end_date = c("14/02/2023", "14/02/2023")
)
```
